% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Omitted as the resume will be in English
%\usepackage{zh_CN-Adobefonts_internal} % Omitted as well

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Weihao Tu}

\basicInfo{
  \email{wy1171633763@163.com} \textperiodcentered\
  \phone{(+86) 17346651272} \textperiodcentered\
  \github[Try2beby]{https://github.com/Try2beby}}

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{Fudan University, School of Big Data}, Shanghai, China}{Sep. 2023 -- Present}
\textit{Master's student} in Applied Statistics, expected graduation June 2025
\begin{itemize}
  \item Main courses: Concepts and Technologies of Knowledge Graphs, Data Mining, Neural Networks and Deep Learning, Social Network Analysis
\end{itemize}

\datedsubsection{\textbf{Beihang University, School of Mathematical Sciences}, Beijing, China}{Sep. 2019 -- Jun. 2023}
\textit{Bachelor's} in Information and Computing Science
\begin{itemize}
  \item Main courses: Basics of Computer (Python), Data Structures, Probability Theory, Mathematical Statistics, Optimization Theory and Algorithms
  \item GPA: 3.81/4.0, Rank: 1/10
  \item Honors and Awards:
        \begin{itemize}
          \item National Scholarship (2019-2020), National Motivation Scholarship
          \item First Prize in the Beijing Division of the National College Student Mathematics Modeling Competition, Honorable Mention in the American Mathematical Modeling Contest
          \item School Academic Excellence Scholarship, Outstanding Student at School Level
        \end{itemize}
\end{itemize}

\section{\faUsers\ Experience}
\datedsubsection{\textbf{Knowledge Graph Construction for Deep Learning Book}}{Dec. 2023}
\begin{itemize}
  \item Workflows: Entity extraction, relationship extraction; entity cleaning, entity alignment; knowledge graph visualization.
  \item Utilized GPT to generate a dataset for entity extraction in the fields of mathematics/computer science, fine-tuned BERT for extraction across the entire book.
  \item Employed edit distance and semantic embedding as metrics, with the assistance of GPT-4 for entity alignment.
  \item Responsible for testing the Rebel model's extraction effects, constructing training datasets, fine-tuning BERT, and frontend visualization of the knowledge graph.
\end{itemize}

\datedsubsection{\textbf{National College Student Mathematics Modeling Competition}}{Sep. 2021}
\begin{itemize}
  \item Utilized Principal Component Analysis for supplier scoring; solved multi-objective planning problem with priority method for supplier selection; used 0-1 integer programming for the transportation scheme. Awarded First Prize in the Beijing Division.
  \item Responsible for data handling (Pandas), programming modeling (Matlab), completed the main part of the programming work.
\end{itemize}

\datedsubsection{\textbf{Graduation Thesis on Dual Theory Training Algorithms in Deep Learning}}{Feb. 2023 -- May 2023}
\begin{itemize}
  \item Implemented an MGD algorithm for solving Minimax problems with coupled linear constraints applied to neural network training.
  \item Developed a problem structure for the dual problem of neural network training issues within the cut-plane algorithm, optimizing the solution process and reducing solution time by 90%.
\end{itemize}

\section{\faUniversity\ Teaching Assistant}
\datedsubsection{\textbf{Teaching Assistant for the "Fundamentals of Computer Science (Science)"}}{Mar. 2021 -- Jul. 2021}
\begin{itemize}
  \item Number of students in the course: about 400, programming language used: Python.
  \item Provided weekly online and offline Q\&A sessions to assist students with debugging; graded lab reports and major assignments.
\end{itemize}

\section{\faCogs\ Skills}
\begin{itemize}
  \item Programming: Proficient in Python, proficient in C and SQL, familiar with data structure concepts, basic automation with Bash scripting; comfortable with Linux platform.
  \item Machine Learning:
        \begin{itemize}
          \item Completed Andrew Ng's Deep Learning series on Coursera and familiar with building and training neural networks using PyTorch.
          \item Completed the Stanford CS229 (Machine Learning) online course, understanding theoretical foundations and implementations of common machine learning algorithms.
        \end{itemize}
  \item Languages: English - Fluent (CET-4 590, CET-6 512), Mandarin - Native speaker.
\end{itemize}

\end{document}